   ---
title: "p8105_hw6_sk5152"
author: "Shuting Kang"
date: "2022-12-01"
output: github_document
---
```{r}
library(tidyverse)
library(dplyr)
library(modelr)
```
## Problem 1 
For this problem, we’ll use the 2017 Central Park weather data that we’ve seen elsewhere. The code chunk below (adapted from the course website) will download these data.
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
## Problem 2

```{r}
raw_data<-read_csv(file="./data/homicide-data.csv")%>%
  janitor::clean_names()
raw_data
```
describe the raw data: 

`r nrow(raw_data)` observations and `r ncol(raw_data)` variables, included `r names(raw_data)`

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. I creata homicides_status binomial variable, 1 represent solved and 0 represent unsolved.

Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric. 


```{r}
homicides_df<-
  raw_data%>%
  mutate(
    city_state=str_c(city,',',state),
    homicides_status=if_else(disposition=="Closed by arrest",1,0),
    victim_age=as.numeric(victim_age)
    )%>%
  filter(city_state!=c("Dallas,TX","Phoenix,AZ","Kansas City,MO","Tulsa,AL"),
         victim_race==c("White","Black"))%>%
  drop_na(victim_age)
homicides_df
```
For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.
```{r}
homicides_Baltimore<-
  homicides_df%>%
  filter(city_state=="Baltimore,MD")


fit=glm(homicides_status~victim_age+victim_sex+victim_race,family = binomial(),homicides_Baltimore)

```

```{r}
Male_Baltimore<-fit%>%
  broom::tidy(conf.int=TRUE,conf.level=0.95)%>%
  filter(term=="victim_sexMale")%>%
  mutate(
    odd_ratio=estimate,
    adjusted_odd_ratio=exp(estimate),
    conf_low=exp(conf.low),
    conf_high=exp(conf.high)
  )%>%
  select(term,odd_ratio,adjusted_odd_ratio,conf_low,conf_high)%>%
  knitr::kable(digits=3)

Male_Baltimore
```


Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}
homicide_all_cities = 
  homicides_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    reg_model = purrr::map(data, ~glm(homicides_status ~ victim_age + victim_sex + victim_race, data =., family = binomial())),
    results = purrr::map(reg_model,~broom::tidy(.x,conf.int=TRUE,conf.level=0.95))
  ) %>% 
  select(-data, -reg_model) %>% 
  unnest(results) %>% 
  mutate(
    adjusted_odd_ratio = exp(estimate),
    conf_low = exp(conf.low),
    conf_high = exp(conf.high)
    ) %>% 
  filter(str_detect(term,"Male")) %>% 
  select(city_state,adjusted_odd_ratio, conf_low, conf_high)
homicide_all_cities

```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
```{r}
homicide_plot<-
homicide_all_cities %>% 
  mutate(
    city_state = fct_reorder(city_state, adjusted_odd_ratio)
  ) %>% 
  ggplot(aes(x = city_state, y = adjusted_odd_ratio, color = city_state)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) + 
  theme(legend.position = "none") + 
  theme(axis.text.x = element_text(size=6, angle=90, hjust = 1)) + 
  labs(
    x = "City_State",
    y = "Adjusted Odd Ratio",
    title = "Estimated ORs and CIs for Each City"
  )
homicide_plot
```

comments:

## Problem 3

 will analyze data gathered to understand the effects of several variables on a child’s birthweight. This dataset, available here, consists of roughly 4000 children and includes the following variables:

babysex: baby’s sex (male = 1, female = 2)
bhead: baby’s head circumference at birth (centimeters)
blength: baby’s length at birth (centimeteres)
bwt: baby’s birth weight (grams)
delwt: mother’s weight at delivery (pounds)
fincome: family monthly income (in hundreds, rounded)
frace: father’s race (1 = White, 2 = Black, 3 = Asian, 4 = Puerto Rican, 8 = Other, 9 = Unknown)
gaweeks: gestational age in weeks
malform: presence of malformations that could affect weight (0 = absent, 1 = present)
menarche: mother’s age at menarche (years)
mheigth: mother’s height (inches)
momage: mother’s age at delivery (years)
mrace: mother’s race (1 = White, 2 = Black, 3 = Asian, 4 = Puerto Rican, 8 = Other)
parity: number of live births prior to this pregnancy
pnumlbw: previous number of low birth weight babies
pnumgsa: number of prior small for gestational age babies
ppbmi: mother’s pre-pregnancy BMI
ppwt: mother’s pre-pregnancy weight (pounds)
smoken: average number of cigarettes smoked per day during pregnancy
wtgain: mother’s weight gain during pregnancy (pounds)


Stage1:Load the raw data 

```{r}
raw_data2<-read.csv(file = "./data/birthweight.csv")
raw_data2
```
clean the data for regression analysis
1. convert categorical variable from numeric type to factor: 
babysex,frace,malform,mrace
2.check the missing
```{r}
clean_data<-
  raw_data2%>%
  mutate(
    babysex=as.factor(babysex),
    frace=as.factor(frace),
    malform=as.factor(malform),
    mrace=as.factor(mrace)
  )%>%
  drop_na()%>%
  select(-pnumlbw,-pnumsga)
clean_data
  
```

propose a regression model for birthweight. 

choose the reasonable variables based on the correlation map, I decided to choose the top five variables that most related to the bwt (target variable).
bhead,blength,frace,gaweeks,and mrace.

```{r}
clean_data2<-
  raw_data2%>%
  janitor::clean_names()%>%
  select(-pnumlbw,-pnumsga)%>%
  drop_na()
corrplot(cor(clean_data2),method='color',order='alphabet')
clean_data2
```
our regression model
```{r}
model_1<-lm(bwt ~ bhead+blength+gaweeks+frace+mrace, data = clean_data)
summary(model_1)

model_1_plot<-
  modelr::add_residuals(model_1)%>%
  modelr::add_predictions(model_1)%>%
  ggplot(aes(x=pred,y=resid))+
  geom_point()+
  geom_smooth(method="lm")
```


show a plot of model residuals against fitted values- use add_predictions and add_residuals in making this plot 
```{r}
fit_1<-lm(bwt ~ bhead + blength + gaweeks+ frace + mrace, data = clean_data)
fit_1_plot<-
  modelr::add_residuals(fit_1)%>%
  modelr::add_predictions(fit_1)%>%
  ggplot(aes(x=pred,y=resid))+
  geom_point()+
  geom_smooth(method="lm")
  
```

compare my model to two others 

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
cv

```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.
